Clearance Project - 1 - Data Generation

### 2025-07-08 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated Rmarkdown files and moved some RDS data files used.

```{r chemical-lists}
human_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "3compartment2",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings()

rat_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                species = "rat",
                                model = "3compartment2",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings()

>>>>

```{r chemical-lists}
human_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "gas_pbtk",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings()

rat_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                species = "rat",
                                model = "gas_pbtk",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings()
